Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
minor changes to section V

Here, with the aim of better balancing the influence of salient sound events and texture-like sounds on the final decision, the similarity between two scenes is computed based on the similarity of their centroid.

@@

The $\widehat{\EMD}$ variant of $\EMD$ is adapted for non-normalized histograms. To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $p_u$ and $p_v$ made of $n$ and $m$ clusters respectively, the $\widehat{\EMD}$ is computed by solving the following linear programming problem:
\begin{equation}
\begin{split}
\widehat{\EMD}(p_u,p_v) &=\left( \min\limits_{\lbrace f_{nm}\rbrace} \sum\limits_{n,m} f_{nm}D_{nm}^{uv} \right) \\
&+ \left|\sum\limits_{n} w_n^u - \sum\limits_{m} w_m^v  \right| \alpha \max\limits_{n,m}\lbrace  D_{nm}^{uv}\rbrace
\end{split}
\end{equation}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n$th bin to ``supply the demand'' of the $m$th bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=\boldsymbol{1}-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$, respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

>>>>

Here, with the aim of better balancing the influence of salient sound events and texture-like sounds on the final decision, the similarity between two scenes is computed based on the similarity of their centroids.

@@

The $\widehat{\EMD}$ variant of $\EMD$ is adapted for non-normalized histograms. To compute the $\widehat{\EMD}$, we use the implementation proposed in \cite{pele2009fast}. Given two signatures $p_u$ and $p_v$ made of $n$ and $m$ clusters respectively, the $\widehat{\EMD}$ is computed by solving the following linear program:
\begin{equation}
\begin{split}
\widehat{\EMD}(p_u,p_v) &=\left( \min\limits_{\lbrace f_{nm}\rbrace} \sum\limits_{n,m} f_{nm}D_{nm}^{uv} \right) \\
&+ \left|\sum\limits_{n} w_n^u - \sum\limits_{m} w_m^v  \right| \alpha \max\limits_{n,m}\lbrace  D_{nm}^{uv}\rbrace.
\end{split}
\end{equation}

@@

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n^{\textrm{th}}$ bin to ``supply the demand'' of the $m^\textrm{th}$ bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=\boldsymbol{1}-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$, respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.
